\section{Objective / 目标}
The \textbf{EY Open Science Data Challenge 2026} focuses on a critical global issue: \textbf{Optimizing Clean Water Supply}. The primary objective is to develop robust machine learning models capable of predicting water quality across various river locations in South Africa.

\textbf{EY Open Science Data Challenge 2026} 聚焦于一个关键的全球问题：\textbf{优化清洁水供应}。主要目标是开发稳健的机器学习模型，预测南非各地河流的水质状况。

Participants must predict three key water quality parameters:
参赛者必须预测三个关键的水质参数：

\begin{enumerate}
    \item \textbf{Total Alkalinity / 总碱度}: Measures the water's ability to neutralize acids. (衡量水体中和酸的能力)
    \item \textbf{Electrical Conductance / 电导率}: Indicates the concentration of dissolved salts. (指示溶解盐的浓度)
    \item \textbf{Dissolved Reactive Phosphorus / 溶解性反应磷}: A nutrient often associated with pollution and agricultural runoff. (一种通常与污染和农业径流相关的营养物质)
\end{enumerate}

\section{Background / 背景}
Clean water is essential for life, yet pollution and climate change threaten water sources globally. By leveraging satellite imagery (Landsat), climate data (TerraClimate), and ground-level measurements, this challenge aims to identify key factors influencing water quality and predict future conditions to aid in sustainable water management.

清洁水对生命至关重要，但污染和气候变化威胁着全球水源。通过利用卫星图像 (Landsat)、气候数据 (TerraClimate) 和地面测量数据，本次挑战旨在识别影响水质的关键因素，并预测未来状况，以协助可持续的水资源管理。

\section{Timeline / 时间表}
\begin{center}
\begin{tabular}{|l|l|}
\hline
\textbf{Milestone / 里程碑} & \textbf{Date / 日期} \\ \hline
Enrollment Opens / 报名开始 & January 20, 2026 \\ \hline
Evaluation Start / 评估开始 & March 14, 2026 \\ \hline
Finalists Announced / 决赛名单公布 & April 1, 2026 \\ \hline
Challenge Ends / 挑战结束 & May 6, 2026 \\ \hline
\end{tabular}
\end{center}

\begin{infobox}[title=Snowflake Summit / Snowflake 峰会]
Top-performing teams using the Snowflake platform will be invited to the Snowflake Summit in San Francisco, June 1-4, 2026.

使用 Snowflake 平台表现优异的团队将受邀参加 2026 年 6 月 1 日至 4 日在旧金山举行的 Snowflake 峰会。
\end{infobox}
